Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 paper.Rnw
found a small mistake in the code

# Load the bullet matching training data and make some adjustments:
#   1. filter out observations known to have tank rash
#   2. exclude features not used to train the rtrees random forest 
#   3. add a case variable
#   4. change the name of the same_source variable to match the test data
#   5. reorder the variables
bullet_train <-
  read.csv("data-bullet-train.csv") %>%
  filter(!(
    land_id1 %in% c(
      "Hamby173-Br6-B2-L1",
      "Hamby173-Br9-B2-L4",
      "Hamby173-BrUnk-BB-L2",
      "Hamby173-BrUnk-BQ-L4"
    ) |
      land_id2 %in% c(
        "Hamby173-Br6-B2-L1",
        "Hamby173-Br9-B2-L4",
        "Hamby173-BrUnk-BB-L2",
        "Hamby173-BrUnk-BQ-L4"
      )
  )) %>%
  select(-lag, -abs_lag, -signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())

>>>>

# Load the bullet matching training data and make some adjustments:
#   1. filter out observations known to have tank rash
#   2. exclude features not used to train the rtrees random forest 
#   3. add a case variable
#   4. change the name of the same_source variable to match the test data
#   5. reorder the variables
bullet_train <-
  read.csv("data-bullet-train.csv") %>%
  filter(!(
    land_id1 %in% c(
      "Hamby173-Br6-B2-L1",
      "Hamby173-Br9-B2-L4",
      "Hamby173-BrUnk-BB-L2",
      "Hamby173-BrUnk-BQ-L4"
    ) |
      land_id2 %in% c(
        "Hamby173-Br6-B2-L1",
        "Hamby173-Br9-B2-L4",
        "Hamby173-BrUnk-BB-L2",
        "Hamby173-BrUnk-BQ-L4"
      )
  )) %>%
  select(-lag, -abs_lag, -overlap, -signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())
